---
title: "Smell evolution analysis"
author: "Darius Sas"
date: "February 26, 2019"
output: html_document
runtime: shiny
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("as-history-all/plotting.R")
options(shiny.maxRequestSize = 100*1024^2)
```
Select an input file and click the "Start analysis" button. Next, after selecting the characteristic which signal to analyse.
```{r fileinput, echo=FALSE}
inputPanel(         
  fileInput("dataset", "Choose a file", 
            accept = c("text/csv","text/comma-separated-values,text/plain",".csv")),
  actionButton("calculate", "Start analysis"))
data <- eventReactive(input$calculate, {read.csv(input$dataset$datapath)})
characteristic <- eventReactive(input$compute, {input$characteristic})
data.sig <- reactive({
    df <- data()
    char <- characteristic()
    signalType <- classifiableSignals[classifiableSignals$signal == char, "type"]
    if (signalType != "generic") {
      df <- df[df$smellType == as.character(signalType), ]  
    }

   return(classifySignal(df, char))
})

data.corr <- reactive({
  df <- data()
  df.corr <- computeCharacteristicCorrelation(df, c("generic"))
  df.corr$var <- paste(df.corr$var1, "and", df.corr$var2)
  return(df.corr)
})
```

Some descriptive statistics
```{r descriptiveStat, echo=FALSE}
renderPlot({  
  plotSmellCountPerVersion(data())
}, height=1000)

```

```{r descriptiveStat2, echo=FALSE}
renderPlot({
  plotBoxplotsSmellGenericCharacteristics(data())
}, height = 1000)
renderPlot({
  plotBoxplotsSmellSpecificCharacteristics(data())
}, height = 1000)
renderPlot({
  plotCycleShapesCountPerVersion(data())
}, height = 1000)
 
```

# Research question 1
## Smell characteristic trend analysis
Click "Compute" and wait for the computation to complete and the plots to appear.
```{r characteristicSelection, echo=FALSE}
inputPanel(uiOutput("characteristicSelector"))
```
The analysed signal is shown below as a matrix of pie plots. Each row is a different project,  whereas columns are the different smell types.
The first row shows the data grouped for all projects.
```{r signalAnalysis, echo=FALSE}
renderUI({
    df <- data()
    inputPanel(
      selectInput("characteristic", "Select a signal to classify", signalNames, selected = "size"),
      actionButton("compute", "Compute"))
})

renderPlot({
    plotSignalTrendCharacteristicAllProjects(df.sig())
}, height = 500)
```

```{r signalAnalysis2,echo=FALSE}
renderPlot({
  plotSignalTrendCharacteristic(data.sig())
}, height = 500)
```

The plot below, instead, shows us the correlation between the classifications of the selected signal and the age of that smell.
For each test performed, p-values are shown only if less than ```0.05```.
```{r iccor, echo=FALSE}
renderPlot({
    plotSignalTrendCorrelationWithAge(data.sig())
})
```

```{r charatrend, echo=FALSE}
renderPlot({
  plotCharacteristicEvolutionTrend(data(), characteristic())
}, height = 900)
```

## Smell-generic characteristics correlation
The correlation between the smell-generic characteristics is depicted below
```{r charcorr,echo=FALSE}
renderPlot({
  plotCharacteristicCorrelationBoth(data.corr())
}, height = 1000)
```

```{r charcorr3,echo=FALSE}
renderPlot({
  plotCharacteristicDistribution(data(), characteristic())
}, height = 900)
```

# Research question 2
## Smell survival analysis
This analysis computes the survival probability for each smell type in each project.
```{r survival, echo=FALSE}
renderPlot({
  plotSurvivalProbabilities(data())
}, height = 900)
```

Whereas the following plot shows the age density for each project
```{r agedensity, echo=FALSE}
renderPlot({
  plotAgeDensity(data())
}, height = 900)
```

And the lifetime of each smell detected in the system
```{r smelllifetime, echo=FALSE}
renderPlot({
  plotSmellLifetimeLines(data())
}, height = 900)
```

